---
  title: "Untitled"
output: html_document
date: "2023-01-20"
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
setwd("C:/Users/Usuario/Desktop/R/VOINEAGU_GSE28521")
options(stringAsFactors=FALSE)
library(BiocManager)
library(GEOquery)
library(Biobase)
library(WGCNA)
library(ggplot2)
```

```{r}
load(file="Clean data (allData and datExpr) 14Dic.RData")
load(file="phenoData and num_phenoData.RData")
load(file="phenoData_binarized.RData")
```


3.1. Sample Clustering

```{r}

#datExpr=cbind(phenoData,t(datExpr))#contiene los datos de expresión + área cerebral y disease status



#Next we cluster the samples (in contrast to clustering genes that will come later) to see if there are any obvious
#outliers.

## Plot the sample tree: Open a graphic output window of size 12 by 9 inches
# The user should change the dimensions if the window is too large or too small.

#matriz de distancias
dMatrix=as.matrix(dist(datExpr, method = "euclidean", diag=TRUE, upper=TRUE))

dMatrix[(1:5),(1:5)]
sampleTree=hclust(dist(datExpr,method="euclidean"), method="complete")
# con el método average (UPGMA): la distancia intercluster es la media de todas las distancias entre todos los puntos de los clusteres (los puntos de un cluster por un lado y los del otro, por otro lado). 

sizeGrWindow(12,9)
par(cex=0.6) #tamaño de la letra de las sample labels
par(mar = c(5,7,7,0))
plot(sampleTree, main = "Sample clustering to detect outliers", sub="", xlab="",
     cex.lab = 2,
     cex.axis = 1.5,
     cex.main = 2
)

rect.hclust(sampleTree, h=60)
#abline(h=60, col="blue")


clust=cutreeStatic(sampleTree, cutHeight=90, minSize=9)
table(clust)

#REMOVE SMPLE OUTLIERS AND SAVE THEM IN ANOTHER MATRIX (outSamples)

keepSamples=(clust!=0) #remove the two outlier samples (which belong to cluster 0)
outSamples=(clust==0)

outDatExpr=datExpr[outSamples,] #save matrix containing outliers
datExpr=datExpr[keepSamples,] #save only rows below the cut line, and all genes (columns)

dim(outDatExpr)
dim(datExpr)

printFlush("Matrix containing outliers (first 5 columns):")
print(outDatExpr[1:nrow(outDatExpr),(1:5)])

nGenes=ncol(datExpr)
nSamples=nrow(datExpr)
print(nGenes)
print(nSamples)
#The variable datExpr now contains the expression data ready for network analysis.


#remove(phenoData[("GSM706394""GSM706410"),])
outPheno=phenoData[outSamples,]
phenoData=phenoData[keepSamples,]


#check that dimensions of the matrix containing good samples and outliers are right,
#both for datExpr and phenoData
dim(outDatExpr)
dim(datExpr)

printFlush("Matrix containing outliers (first 5 columns):")
print(outDatExpr[1:nrow(outDatExpr),(1:5)])
print(outPheno[1:nrow(outPheno),(1:2)])

```

3. 2. Load clinical data into sample dendrogram (visualize how the clinical traits relate to the sample dendrogram)

```{r}
sampleTree2=hclust(dist(datExpr, "euclidean"), method="average")

#convert traits to color representation
traitColors=labels2colors(phenoData) #numbers2colors #usar signed =TRUE si hay valores negativos.
#signed=FALSE,commonLim=FALSE
#Plot sampleTree2 dendogram with colors
phenoLabels=c("Disease status","Tissue (Brain Region)")
par(cex=0.4)
par(mar = c(0,2,1,0))
plotDendroAndColors(sampleTree2, traitColors,
                    cex.axis = 1.2, cex.main = 2,
                    cex.dendroLabels = 0.9, cex.colorLabels=1.2,
                    cex.lab=2,
                    mar=c(2,10,3,1),
                    #palette.colors(palette="Okabe-Ito"),
                    groupLabels=(phenoLabels),
                    dendroLabels = NULL,
                    main="Sample dendogram and trait heatmap"
)


#In the plot, shown in Fig. 2, white means a low value, red a high value, and grey a missing entry.
#The last step is to save the relevant expression and trait data for use in the next steps of the tutorial.

```

3.3. Soft thresholding and connectivity

```{r}

enableWGCNAThreads()

#function pickSoftThreshold -> Analysis of network topology, helps users in choosing
#proper soft-thresholding power

# generate a vector with elements a= entre uno y 10, b entre 12 y 20, numero par)

powers=c(c(1:10), seq(from =12 , to =20, by=2))

#call network topology analysis function (pickSoftThreshold)
sft=pickSoftThreshold(datExpr,powerVector=powers,verbose = 5)

#plot results:
sizeGrWindow(9,5)
par(mfrow=c(1,2),
    cex.lab=1.2,
    mar=c(3,6,2,2))

cex1=1.3

# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1],-sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)", ylab="Scale-Free Topology Model Ft, signed r^2", type="n", cex.main=1.6, cex.ylab=3,
     main=paste("Scale independence (fig.1a)"));
text(sft$fitIndices[,1],-sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.90,col="red")


# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5], cex.main=1.6,
  xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
  main = paste("Mean connectivity (fig. 1b)"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")

```
beta = 10 proved to be the most suitable to our analysis.


3.4. Module construction

3.4.1. Calculation of adjacency matrix, TOM, and dissTOM
```{r}
adjMatrix=adjacency(datExpr,
                    power=10,
                    type="signed",
                    corOptions=list(use="p"))
TOM2=TOMsimilarity(adjMatrix,
                   TOMType = "signed",
                   TOMDenom="min")

dissTOM2=1-TOM2
```


3.4.2. Step-by-step module construction
```{r}
#for adj. matrix constructed using beta=10 (more suitable according to our scale-free topologyy and connectivity criteria)

geneTree2=hclust(as.dist(dissTOM2), method="average")
dynamicMods2=cutreeDynamic(dendro=geneTree2,
                           distM=dissTOM2,
                           deepSplit = 2,
                           pamRespectsDendro = FALSE,
                           minClusterSize = 30)
                           
                           
table(dynamicMods2)
dynamicColors2=labels2colors(dynamicMods2)

#Build Eigengene network dendrogram
MEsList=moduleEigengenes(datExpr,dynamicColors2,
                         excludeGrey = FALSE,
                         softPower=10)
MEs2=MEsList$eigengenes


signif(cor(MEs2, use="p"),2)
dissimME2=(1-t(cor(MEs2, use="p")))/2
hclustME=hclust(as.dist(dissimME2), method="average")

mergeThres=dynamicMergeCut(n=ncol(datExpr), mergeCor=0.9, Zquantile=2.35)
par(mfrow=c(2,2))
sizeGrWindow(8,6)
plot(hclustME,
     main="Module clustering by dissmilarity\n(1-Pearson correlation coefficient)",
     cex.main=0.8,
     cex.lab=1,
     cex.axis=0.9)
abline(h=mergeThres,lty="dashed",col="red")


mergedMods2=mergeCloseModules(datExpr,
                              dynamicColors2,
                              cutHeight = mergeThres)
mergedMEs2=mergedMods2$newMEs
mergedColors2=mergedMods2$colors
table(mergedColors2)

plotDendroAndColors(dendro=geneTree2,
                    cbind(dynamicColors2,
                          mergedColors2),
                    main="dissTOM-based clustering and module colors\nunmerged + merged",
                    c("Dynamic Tree Cut",
                      "Dynamic, Merged (h=0.105)"),
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05,
                    cex.main=1.6,
                    cex.axis=1.2,
                    cex.colorLabels = 1,
                    mar=c(1,9,3,1))

colorOrder = c("grey", standardColors(50));
#construct numerical labels matching the colors (numbers identify each module)
moduleLabels2 = match(mergedColors2, colorOrder)-1;
#The subtraction of 1 in the moduleLabels = match(moduleColors, colorOrder)-1; command is done to adjust the indices of the moduleLabels object so that they match the indexing of the colorOrder vector. The match() function returns the index of the first match of the moduleColors object in the colorOrder vector. However, the indexing of the colorOrder vector starts at 1 (the first color is at position 1, the second color is at position 2, etc), while the indexing of the moduleLabels object should start at 0 (the first module is at position 0, the second module is at position 1, etc). Therefore, subtracting 1 from the indices returned by the match() function is used to shift the indexing of the moduleLabels object by 1, so that the indices match the indexing of the colorOrder vector.


```

3.4.3. plot TOM
```{r}
dissTOM2=1-TOM2
plotdissTOM2=dissTOM2^7
diag(plotdissTOM2)=NA
sizeGrWindow(12,9)
TOMplot(plotdissTOM2, geneTree2,mergedColors2, main="Network heatmap plot\nMerged modules, all genes")
```


5.  Module representation in Multidimensional Scaling Plot
```{r}
cmd1=cmdscale(as.dist(dissTOM2),2)
sizeGrWindow(7,6)
par(mfrow=c(1,1))
plot(cmd1,
     col=as.character(mergedColors2), main="MDS plot",
     xlab="Scaling Dimension 1", ylab="Scaling Dimension 2")

```



3.6.  MODULE-TRAIT RELATIONSHIP
```{r}
mergedMEs=mergedMEs2
mergedColors2=mergedMods2$colors


nGenes=ncol(datExpr)
nSamples=nrow(datExpr)
mergedMEs2=orderMEs(mergedMEs2) #Reorder given (eigen-)vectors such that similar ones (as measured by correlation) are next to each other.

traits=c("DISEASE STATUS", "CEREBELLUM", "FRONTAL CORTEX", "TEMPORAL CORTEX")
  
moduleTraitCor=cor(mergedMEs, binarized_phenoData1, use="p")
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples)#array containing p values

head(moduleTraitCor)
head(moduleTraitPvalue)

sizeGrWindow(9,12)
par(mar=c(2,6,2,1))
# Will display correlations and their p-values
textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
signif(moduleTraitPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(moduleTraitCor)
#par(mar = c(6, 1, 3, 3))

#display correlation values within a heatmap plot

colnames(mergedMEs2)<-gsub("ME","",colnames(mergedMEs2))
                      
labeledHeatmap(Matrix = moduleTraitCor,
xLabels = traits,
yLabels = colnames(mergedMEs),
yColorLabels = TRUE,
ySymbols = names(mergedMEs2),
colorLabels = FALSE,
colors = blueWhiteRed(100),
textMatrix = textMatrix,
setStdMargins = FALSE,
mar=c(2,5,2,1),
cex.text = 0.6,
cex.lab.x = 0.9,
cex.lab.y=1,
zlim = c(-1,1),
xLabelsAngle = 45,
xLabelsPosition = "bottom",
#legendLabel = "Pearson\ncorrelation",
main = paste("Module-trait relationships"))

```

3.7. MODULE SIGNIFICANCE  
Module **significance** to trait (Autism) as average Gene Significance of Genes in the Modules

8a. for ALL GENES, in ALL SAMPLES
```{r}
GS=as.numeric(abs(cor(binarized_phenoData1[,1], datExpr, use ="p")))
ModuleSignificance=tapply(GS, mergedColors2, mean, na.rm=T)
    
sizeGrWindow(10,8)
par(mar=c(7,5,3,1))
plotModuleSignificance(GS, 
                       mergedColors2,
                       boxplot=FALSE,
                       ylab = "Gene significance",
                       ylim=c(0,0.4),
                       cex.axis=1.3,
                       cex.lab=1.2,
                       
                       las = 2,
                       cex.main=1,
                       main="Gene Significance as correlation to clinical condition\n")
                      
                      #main = "Gene significance for Disease Status across modules")

#MODULE SIGNIFICANCE WITH GGPLOT
GS2=as.data.frame(GS, mergedColors2)
#moduleColors=labels2colors(mergedColors2)
#moduleColors=unique(moduleColors)

ylabels=sort(unique(mergedColors2))
ylabels=labels2colors(ylabels)



ggplot(GS2, aes(x=GS, y=mergedColors2, fill=mergedColors2))+
  geom_boxplot()+
  ylab("")+
  xlab("Gene Significance")+
  scale_fill_manual(values=ylabels)+
  ggtitle("")+
  theme(legend.position = "none",
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.x = element_text(size=18))

```



3.8.Functional enrichment analysis 


3.8.a. Selection of gene IDs of relevant modules for GO ENRICHMENT
```{r}
modsOI2=c("orange","lightcyan", "darkturquoise", "darkgrey", "black","darkgreen") 

#Extract genes ENTREZ IDs belonging to each module

orangeModIDs=geneData[,3][mergedMods2$colors=="orange"]
lightcyanModIDs=geneData[,3][mergedMods2$colors=="lightcyan"]
darkturquoiseModIDs=geneData[,3][mergedMods2$colors=="darkturquoise"]
darkgreyModIDs=geneData[,3][mergedMods2$colors=="darkgrey"]
blackModIDs=geneData[,3][mergedMods2$colors=="black"]
darkgreenModIDs=geneData[,3][mergedMods2$colors=="darkgreen"]

#write the gene IDs lists 

lapply(orangeModIDs, write, "orangeModIDs.txt",append=TRUE)
lapply(lightcyanModIDs, write, "lightcyanModIDs.txt",append=TRUE,ncolumns=1)
lapply(darkturquoiseModIDs, write, "darkturquoiseModIDs.txt",append=TRUE)
lapply(darkgreyModIDs, write, "darkgreyModIDs.txt",append=TRUE)
lapply(magentaModIDs, write, "magentaModIDs.txt",append=TRUE)
lapply(darkgreenModIDs, write, "darkgreenModIDs.txt",append=TRUE)
lapply(blackModIDs, write, "blackModIDs.txt",append=TRUE)

```


3.8.b. Plot GO enrichment from data obtained in DAVID

ORANGE
```{r}
GO_orange=read.table("FunAnnotGOBP_orangeModIDs.txt", header=TRUE, sep="\t")
#remove the GO:XXXXXXX from the beginning of the Term
GO_orange$Term<-gsub("GO:\\d{7}~","",GO_orange$Term)
top5_orange=as.data.frame(head(GO_orange,6))
p_top5_orange<-ggplot(data=top5_orange,
       aes(x=reorder(Term,-log10(PValue)),
           y=(-log10(PValue)),
           fill = -log10(PValue)))+
  ylim(0,7)+
  geom_bar(stat="identity" ,position="stack")+
 geom_text(aes(label=paste(round((Count/List.Total*100),digits=2),"%"),
               x = Term, y = -log10(PValue)),
            #position="stack",
            #position_fill(vjust=0.5,reverse=FALSE))+
            #position = position_dodge(width = 1.5), 
            vjust = 0.5, hjust=-0.6) +
  coord_flip()+
  xlab("")+
  ylab("-log10(PValue)")+
  ggtitle("GO Enrichment for ORANGE module")+
  scale_fill_gradient(low="blue",high="red")
plot(p_top5_orange)
```

LIGHTCYAN
```{r}
GO_lightcyan=read.table("FunAnnotGOBP_lightcyanModIDs.txt", header=TRUE, sep="\t")
#remove the GO:XXXXXXX from the beginning of the Term
GO_lightcyan$Term<-gsub("GO:\\d{7}~","",GO_lightcyan$Term)
top5_lightcyan=as.data.frame(head(GO_lightcyan,6))
p_top5_lightcyan<-ggplot(data=top5_lightcyan,
       aes(x=reorder(Term,-log10(PValue)),
           y=(-log10(PValue)),
           fill = -log10(PValue)))+
  ylim(0,7)+
  geom_bar(stat="identity" ,position="stack")+
 geom_text(aes(label=paste(round((Count/List.Total*100),digits=2),"%"),
               x = Term, y = -log10(PValue)),
            #position="stack",
            #position_fill(vjust=0.5,reverse=FALSE))+
            #position = position_dodge(width = 1.5), 
            vjust = 0.5, hjust=-0.6) +
  coord_flip()+
  xlab("")+
  ylab("-log10(PValue)")+
  ggtitle("GO Enrichment for LIGHTCYAN module")+
  
  scale_fill_gradient(low="blue",high="red")
plot(p_top5_lightcyan)
```


DARKTURQUOISE
```{r}
GO_darkturquoise=read.table("FunAnnotGOBP_darkturquoiseModIDs.txt", header=TRUE, sep="\t")
#remove the GO:XXXXXXX from the beginning of the Term
GO_darkturquoise$Term<-gsub("GO:\\d{7}~","",GO_darkturquoise$Term)
top5_darkturquoise=as.data.frame(head(GO_darkturquoise,10))
p_top5_darkturquoise<-ggplot(data=top5_darkturquoise,
       aes(x=reorder(Term,-log10(PValue)),
           y=(-log10(PValue)),
           fill = -log10(PValue)))+
  ylim(0,7)+
  geom_bar(stat="identity" ,position="stack")+
 geom_text(aes(label=paste(round((Count/List.Total*100),digits=2),"%"),
               x = Term, y = -log10(PValue)),
            position="stack",
            #position_fill(vjust=0.5,reverse=FALSE))+
            #position = position_dodge(width = 1.5), 
            vjust = 0.5, hjust=-0.6) +
  coord_flip()+
  xlab("")+
  ylab("-log10(PValue)")+
  
  ggtitle("GO Enrichment for DARKTURQUOISE module")+
  scale_fill_gradient(low="blue",high="red")
plot(p_top5_darkturquoise)

```

DARKGREY
```{r}
GO_darkgrey=read.table("FunAnnotGOBP_darkgreyModIDs.txt", header=TRUE, sep="\t")
#remove the GO:XXXXXXX from the beginning of the Term
GO_darkgrey$Term<-gsub("GO:\\d{7}~","",GO_darkgrey$Term)
top5_darkgrey=as.data.frame(head(GO_darkgrey,6))
p_top5_darkgrey<-ggplot(data=top5_darkgrey,
       aes(x=reorder(Term,-log10(PValue)),
           y=(-log10(PValue)),
           fill = -log10(PValue)))+
  ylim(0,7)+
  geom_bar(stat="identity" ,position="stack")+
 geom_text(aes(label=paste(round((Count/List.Total*100),digits=2),"%"),
               x = Term, y = -log10(PValue)),
            position="stack",
            #position_fill(vjust=0.5,reverse=FALSE))+
            #position = position_dodge(width = 1.5), 
            vjust = 0.5, hjust=-0.6) +
  coord_flip()+
  xlab("")+
  ylab("-log10(PValue)")+
  
  ggtitle("GO Enrichment for DARKGREY module")+
  scale_fill_gradient(low="blue",high="red")
plot(p_top5_darkgrey)


```


DARKGREEN
```{r}
GO_darkgreen=read.table("FunAnnotGOBP_darkgreenModIDs.txt", header=TRUE, sep="\t")
#remove the GO:XXXXXXX from the beginning of the Term
GO_darkgreen$Term<-gsub("GO:\\d{7}~","",GO_darkgreen$Term)
top5_darkgreen=as.data.frame(head(GO_darkgreen,10))
p_top5_darkgreen<-ggplot(data=top5_darkgreen,
       aes(x=reorder(Term,-log10(PValue)),
           y=(-log10(PValue)),
           fill = -log10(PValue)))+
  ylim(0,7)+
  geom_bar(stat="identity" ,position="stack")+
  geom_text(aes(label=paste(round((Count/List.Total*100),digits=2),"%"), #round(a, digits = 2)
                x = Term, y = -log10(PValue)),
            position="stack",
            #position_fill(vjust=0.5,reverse=FALSE))+
            #position = position_dodge(width = 1.5), 
            vjust = 0.5, hjust=-0.6) +
  coord_flip()+
  xlab("")+
  ylab("-log10(PValue)")+
  
  ggtitle("GO Enrichment for DARKGREEN module")+
  scale_fill_gradient(low="blue",high="red")
plot(p_top5_darkgreen)

```

BLACK
```{r}
GO_black=read.table("FunAnnotGOBP_blackModIDs.txt", header=TRUE, sep="\t")
#remove the GO:XXXXXXX from the beginning of the Term
GO_black$Term<-gsub("GO:\\d{7}~","",GO_black$Term)
top5_black=as.data.frame(head(GO_black,10))
p_top5_black<-ggplot(data=top5_black,
       aes(x=reorder(Term,-log10(PValue)),
           y=(-log10(PValue)),
           fill = -log10(PValue)))+
  ylim(0,10)+
  
  geom_bar(stat="identity", position="stack")+
  geom_text(aes(label=paste(round((Count/List.Total*100),digits=2),"%"),
                x = Term, y = -log10(PValue)),
            #Position="stack",
            #position_fill(vjust=0.5,reverse=FALSE))+
            #position = position_dodge(width = 1.5), 
            vjust = 0.5, hjust=-0.6) +
  coord_flip()+
  xlab("")+
  ylab("-log10(PValue)")+
  
  ggtitle("GO Enrichment for BLACK module")+
  scale_fill_gradient(low="blue",high="red")
plot(p_top5_black)

```


3.8.c. Plot GO enrichment for DEGs
```{r}
GO_DEGs=read.table("FunAnnotGOBP_DEGsModIDs.txt", header=TRUE, sep="\t")
#remove the GO:XXXXXXX from the beginning of the Term
GO_DEGs$Term<-gsub("GO:\\d{7}~","",GO_DEGs$Term)
top10_DEGs=as.data.frame(head(GO_DEGs,10))

 
p_top10_DEGs<-ggplot(data=top10_DEGs,
       aes(x=reorder(Term,-log10(PValue)),
           y=(-log10(PValue)),
           fill = -log10(PValue)))+
  ylim(0,7)+
  geom_bar(stat="identity" ,position="dodge")+
  geom_text(aes(label=Count,
                x = Term, y = -log10(PValue)),
            #position="stack",
            #position_fill(vjust=0.5,reverse=FALSE))+
            position = position_dodge(width = 1.5), 
            vjust = 0.5, hjust=-0.6) +
  coord_flip()+
  xlab("")+
  ylab("-log10(pvalue)")+
  ggtitle("GO Enrichment for DEGs in Autistic Temporal Cortex")+
  scale_fill_gradient(low="blue",high="red")
  
plot(p_top10_DEGs)  
  
```


3.9. Module Visualization
```{r}
orangeModIDs0=read.table("orangeModIDs.txt", header=FALSE, sep="\t")
orangeModIDs=orangeModIDs0[,1]

colnames(TOM2)=geneData[,3]
rownames(TOM2)=colnames(TOM2)
select_orange=colnames(TOM2)%in%orangeModIDs

TOM_orange=TOM2[select_orange,select_orange]


#export to VISANT (TOM)
setwd("C:/Users/Usuario/Desktop/R/VOINEAGU_GSE28521/final files/7. Module visualization ")
visOrange=exportNetworkToVisANT(TOM_orange,
                            file="VisInputOrangeTOM.txt",
                            weighted=TRUE,
                            threshold=0.1,
                            probeToGene=NULL)

colnames(adjMatrix)=geneData[,3]
rownames(adjMatrix)=colnames(adjMatrix)

#export to VISANT (ADJ)
select_orange=colnames(adjMatrix)%in%orangeModIDs
adjOrange=adjMatrix[select_orange,select_orange]
setwd("C:/Users/Usuario/Desktop/R/VOINEAGU_GSE28521/final files/7. Module visualization ")
visOrange=exportNetworkToVisANT(adjOrange,
                      file="VisInputOrangeAdj.txt",
                            weighted=TRUE,
                            threshold=0.5,
                            probeToGene=NULL)

#restrict to top 20 connections
#first we have to rename datExpr columns as Gene ID (until now they were named as Gene SYymbol)
colnames(datExpr)=geneData[,3]
nTop=20     #numer of top hub genes to be displayed
IMConn=softConnectivity(datExpr[,colnames(datExpr)%in%orangeModIDs])
top=(rank(-IMConn)<=nTop)
visOrangeTOMTop=exportNetworkToVisANT(TOM_orange[top,top],
                                      file="VisInputOrangeTOMTop.txt",
                                      weighted=TRUE,
                                      threshold=0,
                                      probeToGene=data.frame(geneData$`Gene ID`,geneData$`Gene symbol`))


#LIGHTCYAN
lightcyanModIDs0=read.table("lightcyanModIDs.txt", header=FALSE, sep="\t")
lightcyanModIDs=lightcyanModIDs0[,1]

colnames(TOM2)=geneData[,3]
rownames(TOM2)=colnames(TOM2)
select_lightcyan=colnames(TOM2)%in%lightcyanModIDs

TOM_lightcyan=TOM2[select_lightcyan, select_lightcyan]

#select top expressed genes
colnames(datExpr)=geneData[,3]
nTop=20
IMConn=softConnectivity(datExpr[,colnames(datExpr)%in%lightcyanModIDs])
top=(rank(-IMConn)<=nTop)

visLightcyanTOMTop=exportNetworkToVisANT(TOM_lightcyan[top,top], 
                                         file="VisInputLightcyanTOMTop30.txt",
                                      weighted=TRUE,
                                      threshold=0,
                                      probeToGene=data.frame(geneData$`Gene ID`,geneData$`Gene symbol`))
```



